Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Remove prec/recall equations

\textbf{NER Q.A.}. The NER system outputs a text with tags that enclose the entities. To assess the quality of the
entity extraction, we rely on a technique similar as for the OCR evaluation to build the \emph{NER-target}. The
\emph{NER-target} is different from the groundtruth because it should not involve the errors committed during the
previous stages. The OCR text is first aligned with the groundtruth text to form the NER-\emph{input} (where
\emph{input} is a placeholder for \emph{pero} if the input text is from PERO, NER-\emph{tesseract},
NER-\emph{reference}\ldots). The tags of the groundtruth are then projected in the alignment on NER-\emph{input} to
provide the \emph{NER-target}. The NER system then runs on NER-\emph{input} and outputs the \emph{NER-prediction}. The
precision, recall, and f-measure (or f-score) are computed considering only the exact matches between entities of the
\emph{NER-target} and those from the \emph{NER-prediction}. Precision and recall are defined by \cref{eqn.prec-recall};
the f-measure is their harmonic mean.

\begin{align}
    \mathrm{precision} &= \frac{\text{\#exact matches}}{\text{\#entries in prediction}} & \mathrm{recall} &= \frac{\text{\#exact matches}}{\text{\#entries in reference}}
    \label{eqn.prec-recall}
\end{align}

The evaluation metrics are illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the groundtruth are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.

>>>>

\textbf{NER Q.A.}. The NER system outputs a text with tags that enclose the entities. To assess the quality of the
entity extraction, we rely on a technique similar as for the OCR evaluation to build the \emph{NER-target}. The
\emph{NER-target} is different from the groundtruth because it should not involve the errors committed during the
previous stages. The OCR text is first aligned with the groundtruth text to form the NER-\emph{input} (where
\emph{input} is a placeholder for \emph{pero} if the input text is from PERO, NER-\emph{tesseract},
NER-\emph{reference}\ldots). The tags of the groundtruth are then projected in the alignment on NER-\emph{input} to
provide the \emph{NER-target}. The NER system then runs on NER-\emph{input} and outputs the \emph{NER-prediction}. The
precision, recall, and f-measure (or f-score) are computed considering only the exact matches between entities of the
\emph{NER-target} and those from the \emph{NER-prediction}, i.e. pairs of entries for which the type, start and end positions are exactly the same.
Precision is the ratio of exactly matches divided by the number of predicted entries,
and recall is defined as the ratio of exact matches divided by the number of expected entries;
the f-measure is their harmonic mean.

The evaluation process illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the groundtruth are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.

\joseph{FIXME say we need to discard some entries}
